%-------------------------
% Resume in Latex
% Author : Anuj Prabhu
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

% MY IMPORTS
\usepackage{ragged2e}
\usepackage{graphicx}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% My Custom Commands
\newcommand{\resumeSubheadingEdu}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-7pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Anuj Prabhu} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ (813) 812-9949 ~ \href{mailto:adprabh1@asu.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{adprabh1@asu.edu}} ~ 
    \href{https://www.linkedin.com/in/anujprabhu/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/anujprabhu}}  ~
    \href{https://github.com/anujprabhu01}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/anujprabhu01}} ~ {\raisebox{-0.2\height}\faFlag\ \raisebox{-0.2\height}{U.S. Citizen}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingEdu
    {The Barrett Honors College at Arizona State University}{Aug. 2022 -- May 2026}
      {Bachelor of Science in Computer Science}{Tempe, AZ}
      {Minor in Data Science}{GPA: 4.0 out of 4.0}
      \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Clubs}{: Software Developers Association (SODA), Society of Asian Scientists and Engineers (SASE)} \\
     \textbf{Awards/Distinctions}{: New American University - President's Scholarship, Dean's List 2022 - Present} \\
    }}
 \end{itemize}
  \resumeSubHeadingListEnd

    %-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, R, C/C++, Java, JavaScript/TypeScript, HTML/CSS, MATLAB, Scheme, Bash Script} \\
     \textbf{Technologies/Frameworks}{: Linux, Git, Figma, Node.js, JavaFX, Flutter, MS Office Suite, Google Workspace} \\
     \textbf{Libraries}{: NumPy, Pandas, Matplotlib, Seaborn, Scikit-learn, Beautiful Soup, Tidyverse, Tidymodels, Dplyr, Ggplot2} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {School of Mathematical and Statistical Sciences @ ASU}{August 2024 -- Present}
      {Instructional Aide and Grader}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Served as an Instructional Aide for Statistics, guiding students in data visualization, statistical interpretation, and regression modeling to enhance their analytical and computational skills.}
        \resumeItem{Evaluated Python programs and graded mathematical proofs in Discrete Mathematics, ensuring rigorous logic, algorithmic correctness, and adherence to theoretical concepts.}
        \resumeItem{Partnered with faculty to develop instructional materials and assist in the administration of courses.}
      \resumeItemListEnd

    \resumeSubheading
      {EPICS (Engineering Projects in Community Service) @ ASU}{August 2023 -- Present}
      {Research Lead}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Collaborated with medical experts from Mayo Clinic and Arizona hospitals to grasp user needs and leverage resources.}
        \resumeItem{Conducted comprehensive research on ECMO machines and executed competitive analysis to benchmark the solution.}
        \resumeItem{Led task delegation and collaborated on the design and development of a prototype web application, optimizing team workflow and ensuring high-quality deliverables.}
        \resumeItem{Spearheaded the creation of user personas and journey maps, driving key design decisions and improving overall UX.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ECMO Bridge @ EPICS} $|$ \hspace{0pt} \href{https://ecmo-bridge.vercel.app/}{\underline{\faLink}} \hspace{0pt} $|$ \emph{Node.js, TypeScript, Next.js}}{February 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Developed an extensive, real-time resource-allocation application to match patients in Arizona with available ECMO machines. Generated detailed project documentation, including technical specifications and user guides.}
            \resumeItem{Engineered the centralized ECMO allocation algorithm and contributed to backend development.}
            \resumeItem{Modeled the UI of the prototype web application using Figma and assisted in frontend development.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{NLP-Based Sentiment Analysis of Fortune 500 Tweets} $|$ \emph{R, tidymodels, ggplot2}}{May 2024 -- June 2024}
          \resumeItemListStart
            \resumeItem{Collected and preprocessed Fortune 500 company tweets using \textbf{R}'s \textbf{tm} package, including cleaning and normalization.}
            \resumeItem{Built and fine-tuned a Logistic Regression model with Lasso Regularization using \textbf{tidymodels} and \textbf{glmnet} for tweet sentiment prediction, achieving an \textbf{83\%} accuracy rate.}
            \resumeItem{Visualized key terms and sentiment distributions with word clouds, comparison clouds, and pareto charts using \textbf{ggplot2}, providing actionable insights into public opinion. Documented findings in a comprehensive scientific report.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Predictive Analysis of Online Food Delivery Services} $|$ \emph{Python, scikit-learn, matplotlib}}{April 2024}
          \resumeItemListStart
            \resumeItem{Conducted exploratory data analysis using \textbf{Python}’s \textbf{matplotlib} and \textbf{seaborn} to visualize data distributions and correlations, analyzing demographic factors in relation to customer feedback and order outcomes.}
            \resumeItem{Implemented logistic regression models using \textbf{scikit-learn} and \textbf{statsmodels} to predict customer feedback and order success, performing feature selection and engineering to optimize model performance.}
            \resumeItem{Validated model predictions and assessed their effectiveness in predicting outcomes, identifying key predictors of customer feedback and successful deliveries, and achieving model accuracy rates of \textbf{89\%} and \textbf{88\%} respectively.}
          \resumeItemListEnd
          \vspace{-13pt}
          
        \resumeProjectHeading{\textbf{Other Projects}}{}
        \vspace{-7pt}
        \begin{itemize}
    \small\textbullet \hspace{1pt} Automotive Management System Backend Dev $|$ \emph{C++} \hspace{30pt} \small\textbullet \hspace{1pt} Simplified Engima Encoding Machine $|$ \emph{C++}
        \end{itemize}
          
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

%
%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Completed}{: Programming Languages, OOP, DSA, Exploring Data: R and Python, Applied Statistics, Linear Algebra} \\
     \textbf{Currently Pursuing}{: Foundations of ML, Software Engineering, Human-Computer Interaction, Math for Data Science} \\
    }}
 \end{itemize}


\end{document}